\subsection{Electric Potential}
\hrulefill

\paragraph*{Definition}
Electric potential is the amount of work needed to move a unit charge from a reference point to a specific point in space.
It is measured in volts. The electric potential at a point in space is given by the following equation.

\begin{equation*}
    V = \frac{U_e}{q} = \frac{k_eq}{r}
\end{equation*}

Where $V$ is the electric potential in volts, $U_e$ is the electric potential energy in joules, and $q$ is the charge in coulombs.

\paragraph*{Electric Potential Energy}
Electric potential energy is the energy stored in a system of charges. It is measured in joules. The electric potential energy of a 
system of 2 charges is given by the following equation.

\begin{equation*}
    U_e = q_1V = k_e\frac{q_1q_2}{r}
\end{equation*}

Where $U_e$ is the electric potential energy in joules, $k_e$ is Coulomb's constant, $q_1$ and $q_2$ are the charges in coulombs, and $r$ is the distance between the charges in meters.

\paragraph*{Forces are Derivatives of Potentials}
and the electric force is no different. The electric force is the derivative of the electric potential energy with respect to the distance between the charges. 
We can derive this relationship as follows.

\begin{align*}
    &\quad \vec{F}_e = -\frac{dU_e}{\vec{d\ell}} \quad \Rightarrow \quad \vec{F}_e \cdot \vec{d\ell} = -dU_e \quad \Rightarrow \quad \int \vec{F}_e \vec{d\ell} = -\int dU_e\\
    \Rightarrow& \quad \int \vec{F}_e \vec{d\ell} = -\Delta U_e \quad \Rightarrow \quad W = -\Delta U_e
\end{align*}

Where $\vec{F}_e$ is the electric force in newtons, $\vec{\ell}$ is radial distance from the charge in meters, $\Delta{U_e}$ is the change
in electric potential energy in joules, and $W$ is the work done in joules.

\subsubsection*{Voltage}
Voltage $(\Delta V)$ is the electric potential difference between two points in space. It is measured in volts. The voltage between two points in space is given by the following equation.

\begin{equation*}
    \Delta V = V_b - V_a = \int \vec{E} \cdot \vec{d\ell}
\end{equation*}

Where $\Delta V$ is the voltage in volts, $V_b$ and $V_a$ are the electric potentials at points $b$ and $a$ respectively, $\vec{E}$ is the electric field in newtons per coulomb, 
and $\vec{\ell}$ is the distance between the points in meters.

\paragraph*{Electric Field as a function of Voltage}
The electric field is the derivative of the electric potential with respect to the distance between the charges. We can derive this relationship as follows.

\begin{align*}
    \vec{E} &= \vec{\nabla}V
    \Longrightarrow
    \begin{cases}
        Ex = \frac{\partial V}{\partial x}\\
        Ey = \frac{\partial V}{\partial y}\\
        Ez = \frac{\partial V}{\partial z}
    \end{cases}
\end{align*}