\begin{center}
    \section{Current and Resistance}
    \hrulefill
    \subsection*{Current}
\end{center}

\subsubsection*{Definition}
\hspace{.5cm} Current is defined as the time rate of change of charge through an object. It is measured in amps.

\vbox{
    \center
    $I=\frac{dQ}{dt} \Rightarrow I = nqv_dA$
}\vspace{12pt}

Where $I$ is the current in amps, $n$ is the free electron density in electrons/$m^3$, 
$v_d$ is the drift velocity in $m/s$, and $A$ is the cross-sectional area of the conductor in $m^2$.

\vbox {
    \center
    $[Amps] = [\frac{Coulombs}{second}]$
}


\subsubsection*{Drift Velocity}
Electrons are bouncing around randomly. When an electric field is applied, the bouncing is directed 
in a direction, but it is still chaotic. This bouncing results in heat being generated. Heat is defined 
as the kinetic energy of a particle. The speed of the drift of the electrons is called the drift velocity $(v_d)$.

\vbox{
    \center
    $v_d = \frac{I_{avg}}{nqA} = \frac{I}{nqA}$\\
}\vspace{12pt}

Where $v_d$ is the drift current, n is the free electron density, q is the charge of the current carrier 
(usually an electron) and A is the cross-sectional area of the conductor.


\pagebreak



\subsubsection*{Current Density}
\hspace{.5cm} Current density is the current per unit area. It is defined as:\\
\vbox{
    \center
    $J = \frac{I}{A} = \sigma A = nqv_d$
}\vspace{12pt}

Where $J$ is the current density in $Amps/m^2$, $I$ is the current in amps, $A$ is the cross-sectional 
area of the conductor in $m^2$, $\sigma$ is the conductivity of the material, and $n$ is the free electron 
density in electrons/$m^3$.\\

Voltage can be calculated as a function of current density and conductivity as follows:\\
\vbox{
    \center
    $\Delta V = E\ell = \frac{\ell J}{\sigma}$
}
\vspace{12pt}
\hrulefill

\begin{center}
\subsection*{Resistance}
\end{center}

\subsubsection*{Definition}
Resistance is defined as the ratio of voltage to current, also known as Ohm's law. It is measured in ohms.\\

\vbox{
    \center
    $R = \frac{\Delta V}{I}$
}\vspace{12pt}

Where $R$ is the resistance in ohms, $\Delta V$ is the voltage in volts, and $I$ is the current in amps.\\


\subsubsection*{Resistivity and Conductivity}

\hspace{.5cm} Resistivity is the fundimental property of a material that determines how much it resists the flow of current. 
It is measured in ohm-meters.

\vbox {
    \center
    $\rho = \frac{1}{\sigma} = \frac{RA}{\ell} \Longrightarrow R = \rho \frac{\ell}{A}$
}

\pagebreak

\hspace{.5cm} Conductivity is the inverse of resistivity. It is measured in Siemens per meter. $[S] = [\frac{1}{\Omega}]$\\

\vbox{
    \center
    $\sigma = \frac{1}{\rho} = \frac{\ell}{RA} \Longrightarrow R = \frac{\ell}{R\sigma}$
}
\vspace{16pt}

Where $\rho$ is resistivity, $\sigma$ is conductivity, R is resistance in $\Omega$, $I$ is current in amps, and $\Delta V$ is voltage in volts.

\subsubsection*{Ohmic vs. Non-Ohmic devices}
\hspace{.5cm} Ohmic devices are devices that have a Voltage vs Current slope of $\frac{1}{R}$. Non-ohmic devices have a slope that changes with voltage or current.\\

\subsubsection*{Resistivity and Temperature}

\hspace{.5cm} The resistivity of a material changes with the temperature of the material. The equation for resistivity as a function of temperature is given by:\\

\vbox{
    \center
    $\rho_t = \rho_0[1+\alpha\Delta T]$\\
    \vspace{12pt}
    $\alpha = \frac{\Delta \rho/\rho_0}{\Delta T}$
}
\vspace{12pt}

Where $\rho_t$ is the resistivity of the material at a given temperature, $\rho_0$ is the resistivity of the material at a reference temperature, $\alpha$ is the temperature coefficient (a material constant, much like $\kappa$), $\Delta \rho$ is the change in resistivity, and $\Delta T$ is the change in temperature.\\

\vspace{12pt}
\hrulefill

\begin{center}
\subsection*{Electrical Power}
\end{center}

\subsubsection*{Definition}
\hspace{.5cm} Power is defined as the rate at which energy is transferred or converted. It is measured in watts.\\
\vbox{
    \center
    $P = \frac{dU_e}{dt} = \frac{d}{dt} (Q\Delta V) = \frac{dQ}{dt}\Delta V = I\Delta V$
}

\vbox{
    \center
    $\Longrightarrow P = I^2R = \frac{(\Delta V)^2}{R}$
}
\vspace{12pt}

Where $P$ is power in watts, $Q$ is total charge in Coulombs, $\Delta V$ is voltage in volts, and $I$ is current in amps.